{Automatic Least-Effort Contextual Learning}

### 2017-02-25 etc/paper.tex
fixed IBP description

The automatic attachment follows a least-effort procedure where the new
node's connections are determined using a finite approximation of the Indian
Buffet Process (IBP) \cite{griffiths11}. For every node
$\mathcal{I}_j\in\{\mathcal{I}_i\}_{i=1}^k$ in the context we have $m_j$, a
count of accesses to $\mathcal{I}_j$ since the last context-switch.
Additionally, we define $M=\sum_{i=1}^km_i$ as the total count of knowledge
artifact accesses since the last context-switch. In the IBP, the new node
samples its degree of connectivity from Poisson$(\alpha)$ and attaches to
node $\mathcal{I}_j$ according to Bernoulli$\left(\frac{m_j}{M}\right)$.
% IBP doesn't guarantee non-empty set:
If no connections are made for the new node, a single connection is forced
using an iteration of the Chinese Restaurant Process (CRP) with parameter
$\alpha=0$ and an initial configuration of $k$ tables associated with nodes
in the context where the occupancy of each table is the count of memory
accesses to its corresponding node. This yields the same probability of
selecting a node as the IBP, but guarantees exactly one connection.

>>>>

The automatic attachment follows a least-effort procedure where the new
node's connections are determined using a popular-based probabilistic subset
selection technique equivalent to a non-initial iteration of the Indian
Buffet Process (IBP) with parameter $\alpha=0$ \cite{griffiths11}. For every
node $\mathcal{I}_j\in\{\mathcal{I}_i\}_{i=1}^k$ in the context we have
$m_j$, a count of accesses to $\mathcal{I}_j$ since the last context-switch.
Additionally, we define $M=\sum_{i=1}^km_i$ as the total count of knowledge
artifact accesses since the last context-switch. The new node attaches to
node $\mathcal{I}_j$ according to Bernoulli$\left(\frac{m_j}{M}\right)$.
% IBP doesn't guarantee non-empty set:
If no connections are made for the new node, a single connection is forced
using an iteration of the Chinese Restaurant Process (CRP) with parameter
$\alpha=0$ and an initial configuration of $k$ tables associated with nodes
in the context where the occupancy of each table is the count of memory
accesses to its corresponding node. This yields the same probability of
selecting a node as the IBP, but guarantees exactly one connection.
